Estimating duration in the presence of misclassification

### 2024-03-05 introduction.tex
expand lit review on SPI-M models

Many mechanistic modelling studies were conducted during the pandemic, with at least 100 articles published in the first six months of 2020 alone~\autocite{shankarSystematic}.
In the UK, the most influential were the outputs from SPI-M\todo{cite SPI-M and its outputs - Medley paper?}.
For example, the stages of lifting the lockdown in 2021 each had a set of modelling studies informing the government's decision\todo{cite roadmap 2021 papers}.

Each week, the members of SPI-M would produce a set of estimates of the current state of the epidemic (\eg ther value of $\Re$), known as \emph{nowcasting}.
The nowcasting estimates were based on mechanistic models.
These estimates, once any estimates unduly affected by issues (\eg data quality issues), were statistically combined into a consensus value.\todo{cite SPI-M combination}
The consensus value was published on \url{gov.uk} and informed the government's response to the epidemic.\todo{cite gov.uk R number}

The academic groups contributing estimates used a wide variety of methodologies~\autocite{royalSocietyRnumber}.
These can be split into two types: those based on renewal equations and those based on compartmental models.
Renewal

@@

\Textcite{colmanAscertainment} used CIS prevalence estiamtes to estimate the \emph{ascertainment rate} of community testing (the proportion of all infections that community testing detected).
Their methodology was similar to \textcite{abbottCISincidence}.
\Textcite{colmanAscertainment} do not require a Gaussian process (or other prior) to stabilise incidence estimates because they only estimate the ascertainment rate.
\todo[inline]{Finish writing about \textcite{colmanAscertainment}}

>>>>

Many mechanistic modelling studies were conducted during the pandemic, with at least 100 articles published in the first six months of 2020 alone~\autocite{shankarSystematic}.
In the UK, SPI-M-O (Scientific Pandemic Influenza Group on Modelling, Operational sub-group) was a sub-committee of SAGE (the Scientific Advisory Group for Emergencies), generating evidence based on modelling for policy development~\autocite{medleySPIM,govSPIMO}.
For example, the stages of lifting the lockdown in 2021 each had a set of modelling studies informing the government's decision~\autocite{sageEvidence}.

Each week, the members of SPI-M would produce a set of estimates of the current state of the epidemic (\eg the value of $\Re$), known as \emph{nowcasting}.
The nowcasting estimates were based on mechanistic models.
These estimates, once any estimates unduly affected by issues (\eg data quality issues), were statistically combined into a consensus value~\autocite{parkCombining}.
The consensus value was published on \url{gov.uk} and informed the government's response to the epidemic~\autocite{govRnumber}.
The academic groups contributing estimates used a variety of models, mostly based on either \emph{renewal equations} or \emph{compartmental models}~\autocite{royalSocietyRnumber}.

The renewal equation~\autocite{fraserRenewal} for an infectious disease, in the most general form, is:
\begin{align}
    I(t) &= \int_{0}^{t} \beta(t,\tau) I(t-\tau) d \tau
\end{align}
where $I(t)$ is the mean incidence at time $t$ and $\beta(t, \tau)$ is the instantaneous probability of an individual infected $\tau$ time units ago infects an individual at time $t$.

@@

\Textcite{colmanAscertainment} used CIS prevalence estimates to estimate the \emph{ascertainment rate} of community testing (the proportion of all infections that community testing detected).
Their methodology was similar to \textcite{abbottCISincidence}.
\Textcite{colmanAscertainment} do not require a Gaussian process (or other prior) to stabilise incidence estimates because they only estimate the ascertainment rate.
\todo[inline]{Finish writing about \textcite{colmanAscertainment}}
